Sex differences in upper limb musculoskeletal biomechanics during a lifting task

### 2019-10-21 paper/main.tex
Applied Ergonomics submission

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{lineno}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{natbib}

@@

@@

        \author{Martinez Romain}
        \author{Assila Najoua}
        \author{Goubault Etienne}
        \author{Begon Mickaël}

        \address{School of Kinesiology and Exercise Science, Faculty of Medicine, University of Montreal}

        \begin{abstract}
            %% Text of abstract
            Women experience higher prevalence of work-related upper limb musculoskeletal disorders compared to men.
            Previous studies have investigated the biological, kinematic and electromyographic sex-related differences during a lifting task but the actual differences in musculoskeletal loads remain unknown.
            We investigated the sex differences in three musculoskeletal indicators: the sum of muscle activations, the sum of muscle forces and the relative time spent beyond a shear-compression dislocation ratio.
            A musculoskeletal model was scaled on 20 women and 20 men lifting a 6 or 12~kg box from hip to eye level.
            Women generated more muscle forces and activations than men, regardless of the lifted mass.
            Those differences occurred when the box was above shoulder level.
            In addition, women spent more time beyond a shear-compression dislocation ratio.
            Our work suggests higher musculoskeletal loads among women compared to men during a lifting task, which could be the result of poor technique and strength difference.
        \end{abstract}

        \begin{keyword}
            sex differences \sep upper limb \sep musculoskeletal modeling
            %% keywords here, in the form: keyword \sep keyword

            %% MSC codes here, in the form: \MSC code \sep code
            %% or \MSC[2008] code \sep code (2000 is the default)

        \end{keyword}

@@

    %%
    %% Start line numbering here if you want
    %%
    \linenumbers

    %% main text
    \section{Introduction}
    \label{sec:introduction}
    \input{parts/1-introduction}

    \section{Materials and methods}
    \label{sec:materials-and-methods}
    \input{parts/2-materials-and-methods}

    \section{Results}
    \label{sec:results}
    \input{parts/3-results}

    \section{Discussion}
    \label{sec:discussion}
    \input{parts/4-discussion}

    \section{Acknowledgements}
    \label{sec:acknowledgements}

>>>>

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{lineno}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{float}

@@

    % TODO
    %  - cover letter
    %  - fig

@@

        \author[1]{Martinez Romain\corref{cor1}}
        \ead{martinez.staps@gmail.com}
        \author[1]{Assila Najoua}
        \author[1]{Goubault Etienne}
        \author[1]{Begon Mickaël}

        \address[1]{School of Kinesiology and Exercise Science, Faculty of Medicine, University of Montreal}

        \cortext[cor1]{corresponding author.}

        \begin{abstract}
            Women experience higher prevalence of work-related upper limb musculoskeletal disorders compared to men.
            Previous studies have investigated the biological, kinematic and electromyographic sex-related differences during a lifting task but the actual differences in musculoskeletal loads remain unknown.
            We investigated the sex differences in three musculoskeletal indicators: the sum of muscle activations, the sum of muscle forces and the relative time spent beyond a shear-compression dislocation ratio.
            A musculoskeletal model was scaled on 20 women and 20 men lifting a 6 or 12~kg box from hip to eye level.
            Women generated more muscle forces and activations than men, regardless of the lifted mass.
            Those differences occurred when the box was above shoulder level.
            In addition, women spent more time beyond a shear-compression dislocation ratio.
            Our work suggests higher musculoskeletal loads among women compared to men during a lifting task, which could be the result of poor technique and strength difference.
        \end{abstract}

        \begin{keyword}
            sex differences \sep upper limb \sep musculoskeletal modeling
        \end{keyword}

@@

    \section{Highlights}\label{sec:highlights}
    \begin{itemize}
        \item We investigated sex differences in upper limb musculoskeletal biomechanics during a lifting task.
        \item Women generated higher muscle forces and muscle activations when the box was above shoulder level and spent more time beyond a shear-compression dislocation ratio.
        \item Those musculoskeletal indicators can be used to evaluate work technique and estimate the underlying musculoskeletal loads.
    \end{itemize}

    \section{Introduction}\label{sec:introduction}
    \input{parts/1-introduction}

    \section{Materials and methods}\label{sec:materials-and-methods}
    \input{parts/2-materials-and-methods}

    \section{Results}\label{sec:results}
    \input{parts/3-results}

    \section{Discussion}\label{sec:discussion}
    \input{parts/4-discussion}

    \section{Acknowledgements}\label{sec:acknowledgements}
